Chemistry of the Orphan Stream I: Identifying Stream Members \\ from Low-Resolution Spectroscopy

### 2012-09-19 2012-oss-mrs/draft-oss-mrs.tex
Final version ready for distribution to SK, EM and referee

We have then investigated the status of these ten stars in the PPMXL proper motion catalogue \citep{Roeser;et-al_2010}, finding entries for nine of the candidates. One star (OSS-9 in Table \ref{tab:oss-members}) has a listed proper motion that is different from that of the others at the $6\,\sigma$ level. Consequently, we have reduced the membership likelihood of this star from ``High" to ``Medium".

@@

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/feh.pdf}
	\caption{Metallicities from the Ca\,\textsc{II} triplet lines versus those found from fitting isochrones to the eighteen stars that meet our kinematic and surface gravity criteria. Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim$21.4\,kpc \citep{Newberg;et-al_2010}. Consistency between these methods indicates highly likely stream membership (green region). The minimum isochrone [Fe/H], and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
	\label{fig:feh}
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/cmd.pdf}
	\caption{Color magnitude diagram showing our observed candidates (grey). Observations fulfilling kinematic and gravity cuts are colored by their metallicity, and those with upper limits for surface gravity are marked as triangles ($\triangledown$). Highly probable stream members (see text) are circled. Relevant 10\,Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.63$ at 22.5\,kpc (solid).}
	\label{fig:cmd}
\end{figure}

\section{Conclusion}
\label{sec:conclusions}

@@

@@

\begin{deluxetable}{cccccrlrlcccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{16}
\tablewidth{0pt}
\tablecaption{Identified Orphan Stream Candidates\label{tab:oss-members}}
\tablehead{
	\colhead{Star} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{$g$} &
	\colhead{$g \-- r$} &
	\multicolumn{2}{c}{$\mu_\alpha$} &
	\multicolumn{2}{c}{$\mu_\delta$} &
	\colhead{$V_{hel}$} &
	\colhead{$V_{GSR}$} &
	\colhead{$V_{err}$} &
	\colhead{$EW_{\lambda8807}$} &
	\colhead{[Fe/H]$_{Ca}$} &
	\colhead{[Fe/H]$_{iso}$} &
	\colhead{[Fe/H]\tablenotemark{a}} &
	\colhead{Stream} \\
Name & (J2000) & (J2000) & & & \multicolumn{2}{c}{(mas yr$^{-1}$)} &  \multicolumn{2}{c}{(mas yr$^{-1}$)} & (km s$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & (dex) & Prob.
}
\startdata
OSS-1  & 10:46:21.9 & $+$00:43:21.8 & 17.52 & 0.50 &   4.1 &$\pm$ 4.5 &--34.0 &$\pm$ 4.5 & 209.2 &  73.3 &  9.3 & 0.273 & --1.78 &$<$--2.28& --1.78 & Low \\
OSS-2  & 10:46:29.3 & $-$00:19:38.5 & 17.77 & 0.56 & --1.7 &$\pm$ 4.3 & --2.1 &$\pm$ 4.3 & 217.4 &  78.4 &  5.2 & 0.126 & --1.63 & --1.68  & --1.63 & High \\
OSS-3  & 10:46:50.4 & $-$00:13:15.6 & 17.33 & 0.51 &   1.8 &$\pm$ 4.3 & --5.6 &$\pm$ 4.3 & 215.5 &  77.0 &  4.0 & 0.416 & --1.31 &$<$--2.28& --1.31 & Low \\
OSS-4  & 10:47:06.1 & $-$01:56:03.9 & 18.74 & 0.54 & --6.3 &$\pm$ 4.9 &   4.6 &$\pm$ 4.9 & 218.4 &  74.9 & 17.6 & 0.452 &:--1.12\tablenotemark{b}& --1.40  & --1.40 & High \\
OSS-5  & 10:47:15.0 & $-$03:15:03.9 & 18.66 & 0.54 & --8.2 &$\pm$ 5.2 &   1.7 &$\pm$ 5.2 & 256.8 & 109.5 &  9.0 &$<$0.19&:--1.85\tablenotemark{b}& --1.43  & --1.43 & Medium \\
OSS-6  & 10:47:17.6 & $+$00:25:07.7 & 16.09 & 0.72 & --0.8 &$\pm$ 4.0 &   0.2 &$\pm$ 4.0 & 215.7 &  79.2 &  3.3 & 0.212 & --1.84 & --1.80  & --1.84 & High \\
OSS-7  & 10:47:29.1 & $-$02:02:22.6 & 17.86 & 0.47 &\multicolumn{2}{c}{\nodata}&\multicolumn{2}{c}{\nodata}& 236.9 &  93.2 & 29.8 &$<$0.40& --2.82 &$<$--2.28& --2.82 & High \\
OSS-8  & 10:47:30.1 & $-$00:01:24.5 & 17.25 & 0.61 & --4.0 &$\pm$ 4.2 & --5.2 &$\pm$ 4.2 & 221.3 &  83.6 &  3.5 & 0.123 & --1.62 & --1.68  & --1.62 & High \\
OSS-9  & 10:48:20.9 & $+$00:26:34.4 & 17.88 & 0.55 & --8.1 &$\pm$ 4.3 & --5.4 &$\pm$ 4.3 & 254.9 & 118.9 & 11.7 & 0.467 & --1.65 & --1.73  & --1.65 & High \\
OSS-10 & 10:48:27.8 & $+$00:55:24.0 & 17.72 & 0.51 &--14.4 &$\pm$ 4.6 & --5.3 &$\pm$ 4.6 & 259.1 & 124.5 &  6.7 & 0.182 & --1.48 &$<$--2.28& --1.48 & Low \\
OSS-11 & 10:48:31.9 & $+$00:03:35.7 & 17.02 & 0.58 & --3.6 &$\pm$ 4.1 & --7.7 &$\pm$ 4.1 & 242.3 & 105.1 &  5.1 & 0.234 & --1.12 & --2.10  & --1.12 & Low \\
OSS-12 & 10:48:44.4 & $-$02:53:08.8 & 18.35 & 0.62 & --3.4 &$\pm$ 4.7 & --1.8 &$\pm$ 4.7 & 253.9 & 108.2 &  9.0 & 0.183 &:--1.01\tablenotemark{b}& --1.17  & --1.17 & High \\
OSS-13 & 10:48:46.9 & $-$00:32:27.8 & 17.85 & 0.46 &--28.4 &$\pm$ 4.8 &--12.3 &$\pm$ 4.8 & 248.2 & 109.3 &  8.1 & 0.324 & --2.37 &$<$--2.28& --2.37 & Medium \\
OSS-14 & 10:49:08.3 & $+$00:02:00.2 & 16.27 & 0.62 &   4.9 &$\pm$ 4.0 & --6.0 &$\pm$ 4.0 & 218.5 &  81.5 &  4.6 & 0.034 & --2.70 &$<$--2.28& --2.70 & High \\
OSS-15 & 10:50:13.1 & $+$00:33:52.7 & 16.13 & 0.58 & --3.4 &$\pm$ 4.0 & --7.7 &$\pm$ 4.0 & 229.7 &  94.7 &  5.1 & 0.391 & --1.54 &$<$--2.28& --1.54 & Low \\
OSS-16 & 10:50:24.2 & $-$01:49:05.4 & 17.94 & 0.54 &   3.4 &$\pm$ 4.6 & --2.2 &$\pm$ 4.6 & 252.0 & 109.9 & 25.4 & 0.151 & --1.06 & --1.73  & --1.06 & Low \\
OSS-17 & 10:50:33.8 & $+$00:12:19.1 & 17.82 & 0.60 & --7.4 &$\pm$ 5.0 & --3.3 &$\pm$ 5.0 & 233.5 &  97.5 &  5.9 & 0.596 & --0.90 & --1.43  & --0.90 & Medium \\
OSS-18 & 10:51:19.7 & $+$00:05:15.5 & 17.81 & 0.65 &   4.2 &$\pm$ 4.7 &--11.8 &$\pm$ 4.7 & 218.7 &  82.7 &  5.0 & 0.198 & --1.16 & --1.20  & --1.16 & High 
\enddata
\tablenotetext{a}{Final adopted [Fe/H] value based on quality of two metallicity measurements.}
\tablenotetext{b}{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}
\end{deluxetable}

>>>>

\begin{deluxetable*}{lccccccccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{12}
\tablewidth{0pt}
\tablecaption{Identified Orphan Stream Candidates\label{tab:oss-members}}
\tablehead{
	\colhead{Star} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{$g$} &
	\colhead{$g \-- r$} &
	\colhead{$\mu_{total}$\tablenotemark{a}} &
	\colhead{$V_{GSR}$} &
	\colhead{$EW_{\lambda8807}$} &
	\colhead{[Fe/H]$_{Ca}$} &
	\colhead{[Fe/H]$_{iso}$} &
	\colhead{[Fe/H]\tablenotemark{b}} &
	\colhead{Stream} \\
Name & (J2000) & (J2000) & & & (mas yr$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & (dex) & Prob.
}
\startdata
OSS-1  & 10:46:21.9 & $+$00:43:21.8 & 17.52 & 0.50 &\phn6.1 $\pm$ 6.1 & \phn73.3 $\pm$ \phn9.3 & 0.273 & --1.78 &$<$--2.28& --1.78 & Low \\
OSS-2  & 10:46:29.3 & $-$00:19:38.5 & 17.77 & 0.56 &\phn2.7 $\pm$ 6.1 & \phn78.4 $\pm$ \phn5.2 & 0.126 & --1.63 & --1.68  & --1.63 & High \\
OSS-3  & 10:46:50.4 & $-$00:13:15.6 & 17.33 & 0.51 &\phn5.9 $\pm$ 6.1 & \phn77.0 $\pm$ \phn4.0 & 0.416 & --1.31 &$<$--2.28& --1.31 & Low \\
OSS-4  & 10:47:06.1 & $-$01:56:03.9 & 18.74 & 0.54 &\phn7.8 $\pm$ 6.9 & \phn74.9 $\pm$    17.6 & 0.452 &:--1.12\tablenotemark{c}& --1.40  & --1.40 & High \\
OSS-5  & 10:47:15.0 & $-$03:15:03.9 & 18.66 & 0.54 &\phn8.4 $\pm$ 7.4 &    109.5 $\pm$ \phn9.0 &$<$0.19&:--1.85\tablenotemark{c}& --1.43  & --1.43 & Medium \\
OSS-6  & 10:47:17.6 & $+$00:25:07.7 & 16.09 & 0.72 &\phn0.8 $\pm$ 5.7 & \phn79.2 $\pm$ \phn3.3 & 0.212 & --1.84 & --1.80  & --1.84 & High \\
OSS-7  & 10:47:29.1 & $-$02:02:22.6 & 17.86 & 0.47 &     \nodata      & \phn93.2 $\pm$    29.8 &$<$0.40& --2.82 &$<$--2.28& --2.82 & High \\
OSS-8  & 10:47:30.1 & $-$00:01:24.5 & 17.25 & 0.61 &\phn6.6 $\pm$ 5.9 & \phn83.6 $\pm$ \phn3.5 & 0.123 & --1.62 & --1.68  & --1.62 & High \\
OSS-9  & 10:48:20.9 & $+$00:26:34.4 & 17.88 & 0.55 &\phn9.7 $\pm$ 6.1 &    118.9 $\pm$    11.7 & 0.467 & --1.65 & --1.73  & --1.65 & High \\
OSS-10 & 10:48:27.8 & $+$00:55:24.0 & 17.72 & 0.51 &   15.3 $\pm$ 6.5 &    124.5 $\pm$ \phn6.7 & 0.182 & --1.48 &$<$--2.28& --1.48 & Low \\
OSS-11 & 10:48:31.9 & $+$00:03:35.7 & 17.02 & 0.58 &\phn8.5 $\pm$ 5.8 &    105.1 $\pm$ \phn5.1 & 0.234 & --1.12 & --2.10  & --1.12 & Low \\
OSS-12 & 10:48:44.4 & $-$02:53:08.8 & 18.35 & 0.62 &\phn3.8 $\pm$ 6.6 &    108.2 $\pm$ \phn9.0 & 0.183 &:--1.01\tablenotemark{c}& --1.17  & --1.17 & High \\
OSS-13 & 10:48:46.9 & $-$00:32:27.8 & 17.85 & 0.46 &   30.9 $\pm$ 6.8 &    109.3 $\pm$ \phn8.1 & 0.324 & --2.37 &$<$--2.28& --2.37 & Medium \\
OSS-14 & 10:49:08.3 & $+$00:02:00.2 & 16.27 & 0.62 &\phn7.7 $\pm$ 5.7 & \phn81.5 $\pm$ \phn4.6 & 0.034 & --2.70 &$<$--2.28& --2.70 & High \\
OSS-15 & 10:50:13.1 & $+$00:33:52.7 & 16.13 & 0.58 &\phn8.4 $\pm$ 5.7 & \phn94.7 $\pm$ \phn5.1 & 0.391 & --1.54 &$<$--2.28& --1.54 & Low \\
OSS-16 & 10:50:24.2 & $-$01:49:05.4 & 17.94 & 0.54 &\phn4.0 $\pm$ 6.5 & 109.9    $\pm$    25.4 & 0.151 & --1.06 & --1.73  & --1.06 & Low \\
OSS-17 & 10:50:33.8 & $+$00:12:19.1 & 17.82 & 0.60 &\phn8.1 $\pm$ 7.1 & \phn97.5 $\pm$ \phn5.9 & 0.596 & --0.90 & --1.43  & --0.90 & Medium \\
OSS-18 & 10:51:19.7 & $+$00:05:15.5 & 17.81 & 0.65 &   12.5 $\pm$ 6.6 & \phn82.7 $\pm$ \phn5.0 & 0.198 & --1.16 & --1.20  & --1.16 & High 
\enddata
\tablenotetext{a}{Proper motions and uncertainties in $\alpha$ and $\delta$ added in quadrature.}
\tablenotetext{b}{Final adopted [Fe/H] value based on quality of two metallicity measurements.}
\tablenotetext{c}{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}
\end{deluxetable*}

\begin{figure}[h!]
	\includegraphics[width=\columnwidth]{./figures/feh.pdf}
	\caption{Metallicities from the Ca\,\textsc{II} triplet lines versus those found from fitting isochrones to the eighteen stars that meet our kinematic and surface gravity criteria. Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim$21.4\,kpc \citep{Newberg;et-al_2010}. Consistency between these methods indicates highly likely stream membership (green region). The minimum isochrone [Fe/H], and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
	\label{fig:feh}
\end{figure}

We have investigated the status of these ten stars in the PPMXL proper motion catalogue \citep{Roeser;et-al_2010}, finding entries for nine of the candidates. One star (OSS-13 in Table \ref{tab:oss-members}) has a listed proper motion that is different from that of the other nine members at the $6\,\sigma$ level. Consequently, we have reduced the membership likelihood of this star from ``High" to ``Medium".

@@

\begin{figure}[h!]
	\includegraphics[width=\columnwidth]{./figures/cmd.pdf}
	\caption{Color magnitude diagram showing our observed candidates (grey). Observations fulfilling kinematic and gravity cuts are colored by their metallicity, and those with upper limits for surface gravity are marked as triangles ($\triangledown$). Highly probable stream members (see text) are circled. Relevant 10\,Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.63$ at 22.5\,kpc (solid).}
	\label{fig:cmd}
\end{figure}

@@

\section{Conclusions}
\label{sec:conclusions}

@@

% the final section of acknowledgements, "the University of Washington" does not show if I don't have \phn here.
\phn

@@
